A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-04 report_clean/responce_reviewers.tex

\end{abstract}

\section{General}

We marked corrections suggested by the reviewer 1 in blue, by the reviewer 2 in red, 
and some extra corrections made by us that can be important in green.

More important corrections include
\begin{itemize}
\item changed the wording in the abstract

\item corrected the definition of the cold plasma dielectric tensor, to match the convention $\partial_t\rightarrow -i\omega$ (it had to be hermitian conjugate; 
this had been done everywhere, the corresponding corrections had been made in Table 1 and some figures)

\item corrected the definitions of $\alpha,\delta$ to comply with the definition of the cold plasma dielectric tensor of Stix

@@

(more precisely, removed terms $\frac{\omega^2}{c^2}$ in 
front of them)

\item corrected the formulation of the lemma on the well-posedness and added a remark after the lemma on the sign of $\nu$.

\item corrected assumption on smoothness of $E_y^{\nu}$ in the section 'Numerical Experiments'.

\item shortened slightly the section on limiting amplitude for a non-resonant case.
\end{itemize}

@@

\section{Response to the reviewer 1}

All the corrections are marked in blue.

A. General issues.

1. We agree with the remarks of the reviewer. We included a short introduction into the physics of the problem, 
which hopefully will facilitate in reading the article. 
\begin{itemize}
 \item Concerning Sections 4.1.2, 4.3.1: 
We define more precisely the hybrid resonance now, which in fact requires that $\alpha$ vanishes, 
and $\delta$ does not (while in Section 4.3.1 $\delta$ vanishes as well).
To give a hint on singularity of equations, we cite an article where a simple model problem is considered.

\item 
The notation: 
from now on $\varepsilon^{\nu}_{\omega}(\mathbf{r})$ denotes the cold plasma dielectric tensor, similarly we denote its parameters. 
We added explicitely dependence on space in parameters that depend on the spatial variables.

\item The case $\omega=\omega_c$:
Indeed, $\epsilon_{\infty}<\infty$ if $\omega_c^2\neq \omega^2$, but formally one also needs to require the boundedness of $\omega_p^2$. Therefore we 
added an assumption in the end of the Section Frequency Domain Study on the coefficients of the dielectric tensor, and made a remark on the absence
of the cyclotron resonance. The formulation of Lemma is correspondingly corrected.

\item The limiting amplitude/absorption principle:

A brief description of what limiting absorption and limiting amplitude principles had been added in the end of the introduction.
\end{itemize}

2. 'The reduction to a 1d problem is not clearly justified':  indeed, we changed this in the introduction by adding an assumption on $N_e, B_0$, 
and changed the wording in the introduction to underline that the 1D case is the one of interest.

B. Specific remarks: 
\begin{itemize}
\item p1, abstract: changed

\item p2: in the frequency domain  the problem is regularized by a choice $|\nu|>0$, independently of the sign of $\nu$. 
It is interesting however that for a fixed $\omega$ the limits $\lim_{\nu\rightarrow 0\pm}$ do not result in the same solution. 
In the time domain the sign of $\nu>0$ is indeed of crucial importance for the stability, as well as in Lemma 2.1, provided that $\lambda$ in the 
frequency of the antenna is larger than zero. We added a remark on this before Section 2.1

\item p2, after (1): $L$ is just a non-negative real number. We found it more convenient to place the point of the isolated hybrid resonance in $x=0$.
For $\nu\neq 0$ the energy decays, we added this in the introduction.

\item p3: this should be now fixed in the whole of the article.

\item p3 eq (4): the notation had been changed

\item p4, top: we changed the notation

\item p4, eq. (5) fixed

\item p4, eq. (8): changed the notation in eq (8), though a more general result in Lemma 2.1 is formulated with $u,v$.

\item p4: we changed $\alpha_{\nu}$ to $\beta_{\nu}$ not to confuse with $\alpha$ in the dielectric tensor. The index $\nu$ 
just underlines the dependence of the angle $\beta_{\nu}$ on $\nu$ (indeed, the coercivity result as it is stated, holds for this specific value of $\beta_{\nu}$ defined 
in the end of the proof of the lemma).

\item p. 5: indeed, we changed this

\item p.6:  changed

\item p 6: $Ex$ changed

\item p 8: 'our' code, changed

 \item p.8: fixed section number

 \item p.8 eq (12): added $\nu=0$ + explanation

 \item p.8: added the Airy equation and pointed out the analyticity of the Airy equation. Additionally added a remark on the behaviour of the Airy function to justify the choice of the right boundary 
 condition $\partial_x E=0$.

 \item p.8: the citation had been fixed; we expect $E_y$ to be analytic in this case (since we want it to be equal $\mathrm{Ai}(x)$, this is pointed out right now), 
 and $E_x$ thus is smooth.

 \item  p9, Figure 3: fixed the captions. This had been done for other figures as well. The values $E^{c}_{x,y}$ had been defined in the caption.

 \item p9 on top
  The title of Section 4.1.2 had been changed to Solution of a Frequency-Domain Problem with Resonance

 \item p9 Equation (15,16): changed

 \item p9 after (17): it is really necessary to assume that $H^2$-norm that is bounded, for using the inequality (25). 
 We fixed an assumption on $E_y$, which was incorrect before.

 \item p10 before and after Table 1 : fixed

 \item p 11 Figure 4: fixed

 \item p11 Figure 5:
Agree, fixed. We added a remark in a caption to Figure 4 as well.

\item {\textcolor{red}{p12}}

\item p12 Section 4.3: this explanation had been moved to the introduction

\item p12 Section 4.3.1

@@

  It is true, but in this case there is no resonance, since $\delta(x)\equiv 0$. Hence $E_x=-\frac{i\delta}{\alpha}E_y\equiv 0$, 
  and $E_y$ solves the Airy equation in the frequency domain. We added a small remark to Section 4.3.1 to underline this.

\item p12 Equation (23): it had been removed

\item p14 Figures 8 and 9
Added the captions

\item p15 in Conclusion
  Indeed $P1$!

\item references: corrected
  \end{itemize}

\section{Response to  Reviewer 2}
 \begin{itemize}
\item p2:  We tried to change the wording in the introduction to make it more clear what is a hybrid resonance. 
The singularity appears for $\nu=0$, provided that the diagonal part of the dielectric tensor vanishes and the non-diagonal part does not.

\item 'matricial' had been changed to 'matrix'.

\item p6, 3.1.

@@

We employed the Yee scheme to discretize the problem in the time domain, and the finite element scheme solely for the frequency domain, 
and considered them independently. We added a remark on that in the very beginning of Section 3.

\item p10: mesh multiple times finer. It should be said exactly how many times.

We added a remark that it was at least two times for very fine meshes, and more for coarser ones.

\item {\textcolor{red}{p.12: fixed the typos.}}
\end{itemize}

### 2015-05-04 report_clean/numerics.tex
cosmetics

and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded in $\nu$, together with its derivatives. 

>>>>

and recalling that $\rho_{\nu}=O(x-X_{\nu})$ in the vicinity of the resonance), and is uniformly bounded for sufficiently small $\nu$, together with its derivatives. 
